Automated Synthesis of State-Space Digital Systems

### 2016-12-20 cav2017/cav2017.tex
Revised intro

To this end, we formalise the notion of solution generalisation for
CEGIS and apply CEGAR on simplified abstractions of the system in
order to achieve scalability.  The former technique allows the
inductive generalisation engine to look for candidate solutions in a
reduced solution space.  The latter case is a well know technique for
abstract interpretation that allows simplification of the procedures
over a sound abstraction of the verification model.

>>>>

To this end, we formalise the notion of solution generalisation for
Counter-Example Guided Inductive Synthesis (CEGIS) which makes use 
of Counter-Example Guided Abstraction Refinement (CEGAR)
%on simplified abstractions of the system
in order to achieve scalability.
This strategy enables the inductive generalisation engine inside CEGIS
to look for candidate solutions in a reduced solution space.  %% The
%% latter case is a well know technique for abstract interpretation that
%% allows simplification of the procedures over a sound abstraction of
%% the verification model.
